Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-04-29 ms.tex
phase shift analysis.

>>>>

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.99\textwidth]{images/kepler/phase_shifts.pdf}
\caption{Time Series of phase shifts.}\label{fig:phaseShift}
\end{centering}
\end{figure*}

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/phase_shift_vs_amplitude.pdf}
\includegraphics[width=0.49\textwidth]{images/kepler/phase_shifts_periodogram.pdf}
\caption{Phase shifts versus amplitude (left) and phase shift periodogram (right).}\label{fig:phaseShift}
\end{centering}
\end{figure*}
